Using simulation to optimize the sampling design of fisheries-independent trawl surveys

### 2018-07-12 analysis/paper/sim_survey_paper.Rmd
Add true vs estimated plot to the paper

```{r data, include = FALSE}
library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
load("analysis/cod_sim_exports/2018-07-07_test/test_output.RData")
```

@@

@@

@@

r <- raster::rasterFromXYZ(xyz[, c("x", "y", "N")])
l <- rasterToContour(r, levels = pretty(xyz$N, 20))
df_lines <- suppressWarnings(fortify(l))
levels <- as.numeric(as.character(l$level))
levels <- paste0(levels / 1000, "k")
labs <- levels
labs[seq_along(labs) %% 2 == 0] <- ""
levels <- factor(levels, levels = levels)
names(levels) <- rownames(as.data.frame(l))
df_lines$level <- levels[df_lines$id]

@@

>>>>

```{r data, include = FALSE}
library(SimSurvey)
library(plotly)
library(raster)
library(lattice)
library(viridis)
library(data.table)
load("analysis/cod_sim_exports/2018-07-07_test/test_output.RData")
```

@@

- add population trend plot?

@@

```{r fig_fun}

## http://www.moeding.net/archives/32-Metric-prefixes-for-ggplot2-scales.html
format_si <- function(...) {
  # Format a vector of numeric values according
  # to the International System of Units.
  # http://en.wikipedia.org/wiki/SI_prefix
  #
  # Based on code by Ben Tupper
  # https://stat.ethz.ch/pipermail/r-help/2012-January/299804.html
  # Args:
  #   ...: Args passed to format()
  #
  # Returns:
  #   A function to format a vector of strings using
  #   SI prefix notation
  #

  function(x) {
    limits <- c(1e-24, 1e-21, 1e-18, 1e-15, 1e-12,
                1e-9,  1e-6,  1e-3,  1e0,   1e3,
                1e6,   1e9,   1e12,  1e15,  1e18,
                1e21,  1e24)
    prefix <- c("y",   "z",   "a",   "f",   "p",
                "n",   "µ",   "m",   " ",   "k",
                "M",   "G",   "T",   "P",   "E",
                "Z",   "Y")

    # Vector with array indices according to position in intervals
    i <- findInterval(abs(x), limits)

    # Set prefix to " " for very small values < 1e-24
    i <- ifelse(i == 0, which(limits == 1e0), i)

    paste0(format(round(x/limits[i], 1),
                 trim = TRUE, scientific = FALSE, ...),
          prefix[i])
  }
}
si <- format_si()

@@

r <- raster::rasterFromXYZ(xyz[, c("x", "y", "N")])
l <- rasterToContour(r, levels = pretty(xyz$N, 20))
df_lines <- suppressWarnings(fortify(l))
levels <- as.numeric(as.character(l$level))
levels <- si(levels)
labs <- levels
labs[seq_along(labs) %% 2 == 0] <- ""
levels <- factor(levels, levels = levels)
names(levels) <- rownames(as.data.frame(l))
df_lines$level <- levels[df_lines$id]

@@

```{r est_fig, fig.height = 9, fig.width = 8.5}

which_survey <- 98

d <- sim$age_strat_error
d <- d[d$survey == which_survey & d$sim %in% 1:10, ]
d$age[d$age > 15] <- 15 # aggregate beyond 15
d$age <- as.character(d$age)
d$age[d$age == "15"] <- "15+"
d$age <- factor(d$age, levels = c(as.character(1:14), "15+"))
d <- d[, list(I_hat = sum(I_hat), I = sum(I)), by = c("year", "age", "sim")]

p <- ggplot(data = d) + 
  geom_line(aes(x = year, y = I_hat, color = sim, group = sim), size = 0.3) +
  geom_line(aes(x = year, y = I), color = viridis::viridis(1), size = 0.7) +
  scale_color_viridis(begin = 0.5, guide = FALSE) +
  facet_wrap(~age, scales = "free_y", dir = "v", nrow = 5) +
  xlab("Year") + ylab("Abundance index") +
  theme_minimal() +
  scale_y_continuous(labels = format_si()) +
  scale_x_continuous(expand = c(0.01, 0)) +
  theme(legend.justification = c(0, 1),
        plot.margin = unit(c(0.2, 0.2, 0.2, 0.2), "cm"))

cowplot::save_plot(plot = p, filename = "analysis/paper/figures/true_vs_est.pdf",
                   base_height = 9, base_width = 8.5)
p
